---
title: "Coding"
output: pdf_document
---

# 6.
Here we have that "x1_covariate1" is just the intercept term, so we don't need to include it since we already add intercept in our algorithm.
We use least square estimator of beta to initialize our algorithm.
```{r p6}
myLR <- function(Y, X, it_max=25, eps=1e-8){
    D = cbind(1, X)
    p = dim(D)[2]
    beta = solve(t(D) %*% D) %*% t(D) %*% Y
    prob = exp(D %*% beta) / (1 + exp(D %*% beta))
    for(i in 1:it_max){
        WAUX = diag(array(prob * (1-prob)))
        W = solve(t(D) %*% WAUX %*% D)
        dbeta = W %*% t(D) %*% (Y - prob)
        if(norm(dbeta,"2") <= eps)
            break
        beta = beta + dbeta
        prob = exp(D %*% beta) / (1 + exp(D %*% beta))
    }
    std = sqrt(diag(W))
    result = list(beta = beta, std = std)
    return(result)
}

data = read.csv("Ex0107.txt", sep=" ")
Y = data$y_response
X2 = data$x2_covariate2

fit = glm(Y ~ X2, family = binomial)
result = myLR(Y,X2)

summary(fit)
print(result)
```
And we can see here my estimator consists with R function.


# 7.
```{r p7, message=F, warning=F}
library(magrittr)
library(dplyr)

data2 = read.csv("Ex0109.csv")
counts = aggregate(cbind(Pro05,Anti05,Pro06,Anti06,Pro07,Anti07) ~ Party, data = data2, sum)
print(counts)

X = rbind(c(5,0),
          c(6,0),
          c(7,0),
          c(5,1),
          c(6,1),
          c(7,1))
colnames(X) = c("Year","Party")
Pro = c(2825,1905,3242,346,366,671)
Anti = c(551,332,554,2957,1840,3105)
fit = glm(cbind(Pro,Anti) ~ X, family=binomial)
summary(fit)
```
We can see here the p value for Party is extremely small, so the behavior of two parties towards pro-environment voting is significant different regardless of year effect. 