---
title: "Coding"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
```

## 1
Visualize the data.
```{r visual, message=FALSE,warning=FALSE}
library("nlme")
library("ggplot2")

Raildata = Rail
ggplot(Raildata, aes(x=Rail, y=travel)) +
    geom_boxplot(fill="grey80", color="blue")

```
(a). 
Here's the mean `u`, effects `effects` and test information of fixed effect model:
```{r q1a, message=FALSE,warning=FALSE}
library(dplyr)
u = mean(Raildata$travel)
effects = Raildata %>%
        group_by(Rail) %>%
        summarise(means=mean(travel)-u)
print(u)
print(effects)
summary(aov(travel~Rail, Raildata))
```
(b). Fitted model:
```{r q1b, message=FALSE,warning=FALSE}
library(lme4)
Rail.mixed = lmer(travel ~ 1 + (1|Rail), Raildata)
summary(Rail.mixed)
```
(c).Use the fomula like in 1.2(b) to calculate the BLUPs and compare with results in 2.1(a), we can find that BLUPs is a little shrinked towards zero.
```{r q1c, message=FALSE,warning=FALSE}
sigma_u = 24.805
sigma = 4.021
u = 66.50
BLUPs = Raildata %>%
            group_by(Rail) %>%
            summarise(effects = 3*sigma_u^2/(sigma^2+3*sigma_u^2) * (mean(travel)-u))
print(BLUPs)
```

## 2

(a).
Visualize the data.
```{r q2a, message=FALSE,warning=FALSE}
library(lattice)
data("Pixel")
xyplot(pixel ~ day | Dog + Side, data=Pixel, type='o', pch=20)
```

(b).
We regard the two $\beta_1$ in this question as a typo, we fit three fixed effects $\beta_0,\beta_1,\beta_2$.
Here's the result, it says that the estimates for $\beta_0,\beta_1,\beta_2$ are 1074.496, 4.87216 and -0.24739.
And for the random effect, for `Dog` level, the standard deviation is 22.82; for `Side` within `Dog`, std is 15.70 and for the random error, the std is `12.92`.
```{r q2b, message=FALSE,warning=FALSE}
D = mutate(Pixel,day2=day^2)
fit = lmer(pixel~day+day2+(1|Dog/Side), data=D)
summary(fit)
```