---
title: "Statistical Computing Homework 1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part 1

### Load Data
```{r load_data}
library(datasets)
data(WorldPhones)
WorldPhones
```

### Clean Data
```{r message = FALSE, warning = FALSE, comment = NA}
library(tidyr)
library(dplyr)

WorldPhones %>%
    as.data.frame() %>%
    mutate(year = factor(row.names(WorldPhones))) %>%
    gather(country, number, -year) 
```

## Part 2
### Load Data
```{r load_pm25_data, message=FALSE, warning=FALSE}
library(readr)
data <- read_csv("SPEC_2014.csv.zip")
```
### Preview Data
```{r preview_data,message=FALSE, warning=FALSE}
library(dplyr)
names(data)
head(select(data,c("Sample.Value","Parameter.Name",
                   "State.Name","County.Name","City.Name" )))
```

### Solutions
1.
```{r q1, message=FALSE, warning=FALSE}
data %>%
  filter(Parameter.Name=="Bromine PM2.5 LC", State.Name=="Wisconsin") %>%
  select(Sample.Value) %>%
  summarize(Avg.Value = mean(Sample.Value))
```
So, the average value of “Bromine PM2.5 LC” in the state of Wisconsin is 0.003960482.

2.
```{r q2, message=FALSE, warning=FALSE}
avg.data <- data %>%
  select(c("Parameter.Name","Sample.Value")) %>%
  group_by(Parameter.Name) %>%
  summarize(Avg.Value = mean(Sample.Value))

avg.data

avg.data %>%
  filter(Avg.Value == max(Avg.Value))
```
Therefore "OC CSN Unadjusted PM2.5 LC TOT" has the highest average level.

3.
```{r q3, message=FALSE, warning=FALSE}
data %>%
  select(c("Parameter.Name","Sample.Value",
           "State.Code","County.Code","Site.Num")) %>%
  filter(Parameter.Name == "Sulfate PM2.5 LC") %>%
  filter(Sample.Value == max(Sample.Value))
```
Therefore "State 34 County 001 Site 0006" has the highest levels of “Sulfate PM2.5 LC”.

4. 
```{r q4, message=FALSE, warning=FALSE}
c_a <- data %>%
  select(c("Parameter.Name","Sample.Value","State.Name")) %>%
  filter(Parameter.Name == "EC PM2.5 LC TOR" &
         State.Name %in% c("California","Arizona")) %>%
  group_by(State.Name) %>%
  summarize(Avg.Value = mean(Sample.Value))

c_a

filter(c_a,State.Name=="California")[,"Avg.Value"] - filter(c_a,State.Name=="Arizona")[,"Avg.Value"] 
```
Therefore the average levels of “EC PM2.5 LC TOR” in California is 0.01856696 bigger than that in Arizona.

5. 
```{r q5, message=FALSE, warning=FALSE}
data %>%
  select(c("Parameter.Name","Sample.Value","Longitude")) %>%
  filter(Parameter.Name %in% c("OC PM2.5 LC TOR","EC PM2.5 LC TOR")) %>%
  mutate(Location = factor(Longitude < -100,labels=c("Eastern","Western"))) %>%
  group_by(Parameter.Name, Location) %>%
  summarize(Med.value = median(Sample.Value))
```
Median levels are shown above.

## Part 3

### Load Data
```{r xl, message=FALSE, warning=FALSE}
library(readxl)
EPA <- read_excel("aqs_sites.xlsx")
```

### Preview Data
```{r preview_data2,message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
names(EPA)
head(select(EPA,c("Land Use","Location Setting",
                  "State Name","County Name","City Name" )))
```

### Solutions

1.
```{r q21, message=FALSE, warning=FALSE}
EPA %>%
  select(c("Land Use","Location Setting")) %>%
  rename(Land.Use="Land Use", Location.Setting="Location Setting") %>%
  filter(Land.Use == "RESIDENTIAL" & Location.Setting == "SUBURBAN") %>%
  summarize(Amount = length(Land.Use))
```
Therefore, there are 3527 monitoring sites are labelled as both “RESIDENTIAL” for Land Use and “SUBURBAN” for Location Setting.

2.
```{r q22, message=FALSE, warning=FALSE}
EPA_tidy <- EPA %>%
  select(c("Land Use","Location Setting",
           "State Code","County Code","Site Number")) %>%
  rename(Land.Use="Land Use", Location.Setting="Location Setting")

data <- data %>% 
          mutate(State.Code = as.numeric(State.Code),
                 County.Code = as.numeric(County.Code),
                 Site.Num = as.numeric(Site.Num))

total_data <- inner_join(data, EPA_tidy, by = c("State.Code" = "State Code",
                                                "County.Code" = "County Code",
                                                "Site.Num" = "Site Number"))

total_data %>%
  select(c("Parameter.Name","Sample.Value","Longitude",
           "Land.Use","Location.Setting")) %>%
  mutate(Location = factor(Longitude < -100,labels=c("Eastern","Western"))) %>%
  filter(Location == "Eastern" & 
         Parameter.Name %in% c("OC PM2.5 LC TOR","EC PM2.5 LC TOR") &
         Land.Use == "RESIDENTIAL" &
         Location.Setting == "SUBURBAN") %>%
  group_by(Parameter.Name,Location,Land.Use,Location.Setting) %>%
  summarize(Med.Value = median(Sample.Value))
```
Median values are shown above.